Floquet-Drude Conductivity in Dressed Quantum Hall Systems

### 2021-07-25 paper/v1.0/abstract.tex
Corrections for abstract and introduction

A generalized mathematical model for the transport properties of quantum systems exposed to a stationary magnetic field and a high intensity electromagnetic field is presented. The new formulation, which applies to the two-dimensional dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity approach. We model our system as a two-dimensional electron gas (2DEG) that interacts with two external fields. To analyze the strong light coupling with the 2DEG, we utilize the Floquet theory as a nonperturbative procedure. Moreover, the Floquet Fermi golden rule is adopted to explore the impurity scattering effects against Floquet states in disordered quantum Hall systems. Based on our fully analytical expression and particular graphical representations, we demonstrate that the characteristics of conductivities in two-dimensional quantum Hall systems can be manipulated using a strong light. The outcomes align with the theoretical descriptions which are already well-suited with experimental results and at the same time our theory provides a more generalized analysis on the characteristics of conductivity of quantum Hall systems. Thus, this model more realistically describes that how to employ external strong radiation as a tool to utilize transport properties in various 2D nanostructures which serve as a basis for nano-scale quantum devices.

>>>>

A generalized mathematical model for predicting the transport properties of a quantum system exposed to a stationary magnetic field and a high intensity electromagnetic field is presented. The new formulation, which applies to two-dimensional(2D) dressed quantum Hall systems, is based on Landau quantization theory and Floquet-Drude conductivity approach.
We model our system as a two-dimensional electron gas (2DEG) that interacts with two external fields. To analyze the strong light coupling with the 2DEG, we employ the Floquet theory as a nonperturbative procedure. Moreover, the Floquet Fermi golden rule is adopted to explore the impurity scattering effects against Floquet states in disordered quantum Hall systems.
We derive fully analytical expressions to describe longitudinal components in conductivity tensor in dressed quantum Hall systems and apply the developed model to a numerical evaluation with empirical parameters. Then, we demonstrate that the conductivity characteristics in quantum Hall systems can be manipulated using a strong external light.
Our results align with well-established and experimentally
verified theoretical descriptions for undressed systems while providing a more generalized analysis on the characteristics of conductivity in quantum Hall systems.
Thus, our model can be used to more accurately interpret the employment of external strong radiation as a tool to engineer transport properties in various 2D nanostructures.

### 2021-07-25 paper/v1.0/sections/1_introduction.tex
Corrections for abstract and introduction

Manipulating physical systems as a consequence of light engagements inaugurated an astonishing scope of twentieth-century physics namely quantum optics \cite{grynberg10}.
Quantum optics have dragged research attention in the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21}, sensing \cite{rodrigo2015,pirandola18,hapuarachchi2018}, energy harvesting \cite{yuan16,sun18},
quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and abundant specialities of recent technologies \cite{rivera20}.
The studies on quantum optics of nanostructures were centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, quantum cavity physics \cite{tsang10,devi20}.
However, over the past few years, the foremost aims for examining nanostructures under external radiation were focused on understanding their transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.

The significance of describing fundamental mechanisms taking place in charge transport is that they will pave the way to invent new nanoelectronic devices and optimize their performance \cite{premaratne21}.
Among these works, most studies have acknowledged the driving field as a perturbation field \cite{pervishko15,morina15} that is not applicable for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
When a high intensity electromagnetic field account with a perturbation method, the number of higher-order interaction terms need to be recognized gets escalate. Then a more accurate and powerful concept need to be adopted and we need to treat the interacting fermion system and the radiation as a one unique quantum system (dressed system) \cite{morina15,cohen98,scully01}. On account of the transport characteristics of dressed nanostructures, they are still expecting extensive analysis.

Theoretical analyses of the transport properties of dressed fermions systems were recently reported in Refs. \cite{kibis14,morina15,wackerl20} where a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form in Ref. \cite{wackerl20}, introducing a novel type of Green’s functions namely four-times Green’s functions. As a consequence, the established formalism introduces a novel technique to exploit the transport attributes of nanostructures by an intense dressing field.

At the other end, quantum Hall effect \cite{girvin90} observed for two-dimentional fermions systems at low temperatures under strong stationary magnetic field manifest remarkable magneto-transport behaviors and transport properties of these systems attracted many researches attention in experimental \cite{allerman95,tieke97,pan05} and theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} point of view.
Akira Endo \textit{et al.} \cite{endo09} previously presented, the calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system and these theoretical calculations are well-suited with the experimental observations while other former studies yields a semi-elliptical broadening for Landau levels and gives less fitting interpretations for the empirical results \cite{endo09}.

In contrast, more fascinating transport phenomena can be achieved by creating a quantum Hall system using a nonoscillating magnetic field and simultaneously applying a dressing field.
Whilst there exist a number of leading theories devoted to the calculation of conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of charge transport in the quantum Hall systems.
Furthermore, K. Dini \textit{et al.} \cite{dini16} have recently investigated the one-directional conductivity behavior of dressed quantum Hall systems, and they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system. In their study, they used the conductivity models from Refs. \cite{ando74_1,ando82} and as mentioned in A. Endo \textit{et al.} work \cite{endo09} those models yields a semi-elliptical broadening for Landau levels and gives barely fitting representations for the experimental findings.

In the present analysis, we report a robust mathematical model for dressed two-dimensional electron gas(2DEG) unveiled to another nonoscillating magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of 2DEG system and the orbital motion of electrons becomes completely quantized, and the energy spectrum becomes discrete by creating Landau levels \cite{landau30}.
Such a singular system is known as a two-dimentional quantum Hall system and in this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in the periodically driven quantum Hall systems by developing a generalized analytical description to identify transport characteristics of dressed quantum Hall systems using Floquet-Drude conductivity \cite{wackerl20}.
Finally, we demonstrate that our generalized model is agreed with state-of-the-art conductivity model \cite{endo09} already developed for specialized quantum Hall systems that have been considered without the external dressing field. 
Moreover, optical manipulation can be used as a mechanism to utilize transport behavior in numerous two-dimentional nanostructures which serve as a basis for nanoelectronic devices and we believe that our theoretical analysis and visual depictions of numerical results can be used to understand the basic structure and optimize the performance of nanoscale quantum devices.

The paper is organized as follows. In Sec.  \ref{sec_schrodinger_problem}, we introduce our dressed quantum Hall system and the exact wave function solutions for the given configuration. Sec. \ref{sec_floquet_theory}, provides the Floquet theory interpretation of these wave functions.
We introduce Floquet Fermi golden rule for quantum Hall system in Sec. \ref{sec_inverse_scattering_time}, and we use it in Sec. \ref{sec_floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
The derived theoritical model is further analyzed numerically using empherical system parameters and compared with previous studies in Sec. \ref{sec_manipulate_conductivity}, followed by concluding remarks in Sec. \ref{sec_conclusions}.

>>>>

Manipulating light matter interactions in the quantum regime paved the path for an astonishing number of useful technologies in the twentieth century. Quantum optics, which study these interactions, have drawn research attention in the disciplines of optoelectronics \cite{liu16,wijesekara20,tao21}, sensing \cite{rodrigo2015,pirandola18,hapuarachchi2018}, energy harvesting \cite{yuan16,sun18},
quantum computing \cite{huh15,slussarenko19,andersen21}, bio-information \cite{marais18,bian20}, and many other specialities of recent technologies \cite{rivera20}.
The studies on quantum optics of nanostructures were generally centered on metamaterials \cite{shalaev07,si14}, quantum plasmonic effects \cite{hapuarachchi19,perera20}, lasers and amplifiers \cite{zhang05,chow13}, quantum cavity physics \cite{tsang10,devi20}.
However, in recent years, the foremost aim of examining nanostructures under external radiation was for understanding their electron transport characteristics \cite{kitagawa11,zhou11,kibis14,pervishko15,morina15,dehghani15,dini16,wackerl20}.

Better understanding the fundamental mechanisms of charge transport can allow us to invent novel nanoelectronic devices and optimize their performance \cite{premaratne21}.
Among these works, most studies have considered the driving field as a perturbation field \cite{pervishko15,morina15} However, that assumption breaks down for systems under high-intensity illuminations \cite{grifoni98,wackerl20}.
Modeling an electromagnetic field under a perturbative formalism involves expanding the interaction terms in powers of the field intensity. At high intensities, the higher order terms influence the physics more strongly than the lower order terms, and the basis of the perturbative treatment begins to break down.
Then a more accurate and powerful concept needs to be adopted where we treat  the interacting fermion system and the radiation as one combined quantum system (dressed system) \cite{morina15,cohen98,scully01}.

Theoretical analyses of the transport properties of dressed fermion systems were recently reported in Refs. \cite{kibis14,morina15,wackerl20}.
Furthermore, in Ref. \cite{wackerl20} a general expression for Floquet-Drude conductivity has been derived in a fully closed analytical form, introducing a novel type of Green’s functions namely four-times Green’s functions. This established a novel technique to exploit the transport attributes of nanostructures under an intense dressing field.

Quantum Hall effect \cite{girvin90} observed for two-dimensional fermion systems at low temperatures under strong stationary magnetic fields manifest remarkable magneto-transport behaviors. Transport properties of these systems have recently attracted both theoretical \cite{ando72,ando74_1,ando74_2,ando74_3,ando74_4,ando82,endo09} and experimental \cite{allerman95,tieke97,pan05} interest.
Endo \textit{et al.} \cite{endo09} presented the calculations of longitudinal and transverse conductivity tensor components and their relationship in a quantum Hall system. These theoretical calculations better align with experimental observations compared to previous studies. For instance, former studies yield a semi-elliptical broadening for Landau levels and give less fitting interpretations for the empirical results \cite{endo09}.

In contrast, more interesting phenomena can be observed by simultaneously applying a dressing field to a quantum Hall system under a non-oscillating magnetic field.
Whilst there exist several leading theories for calculating conductivity tensor elements in quantum Hall systems \cite{ando74_1,ando82,endo09}, they have not been utilized to describe the optical manipulation of charge transport.
Recently, Dini \textit{et al.} \cite{dini16} have investigated the one-directional conductivity behavior of dressed quantum Hall systems. However, they have not adopted the state-of-the-art model to describe the conductivity in a quantum Hall system. In their study, they used the conductivity models from Refs. \cite{ando74_1,ando82}, and as mentioned in Endo \textit{et al.} work \cite{endo09}, those models yields a semi-elliptical broadening for Landau levels and gives less agreement with experimental results.

In the present analysis, we present robust mathematical model for dressed two-dimensional electron gas(2DEG) subject to another nonoscillating magnetic field.
A stationary magnetic field is applied perpendicularly across the surface of the 2DEG system and the orbital motion of electrons becomes completely quantized. This causes the orbital motion of the electrons to be quantized, and a discrete energy spectrum with Landau splitting is observed \cite{landau30}.
Such a system is known as a two-dimensional quantum Hall system. In this study, we explicitly calculate the longitudinal  ($\sigma^{xx},\sigma^{yy}$) components of the conductivity tensor in periodically driven quantum Hall systems by developing a generalized analytical description to identify transport characteristics of dressed quantum Hall systems using Floquet-Drude conductivity \cite{wackerl20}.
Finally, we demonstrate that our generalized model reproduces the results of
the state-of-the-art conductivity model in Ref. \cite{endo09}, which was developed for the more specific case of quantum Hall systems without the external dressing field.
Moreover, we find that the optical field can be used as a mechanism to regulate transport behavior in numerous two-dimensional nanostructures which can serve as a basis for nanoelectronic devices. We believe that our theoretical analysis and visual depictions of numerical results will lead to a better understanding of manipulating charge transport. Moreover, this will inspire advanced  developments in nanoscale quantum devices.

The paper is organized as follows. In Sec.  \ref{sec_schrodinger_problem}, we introduce our dressed quantum Hall system and the exact wave function solutions for the given configuration. Sec. \ref{sec_floquet_theory}, provides the Floquet theory interpretation of these wave functions.
We introduce Floquet Fermi golden rule for quantum Hall system in Sec. \ref{sec_inverse_scattering_time}, and we use it in Sec. \ref{sec_floquet_drude_conductivity} to derive analytical expressions for longitudinal components of conductivity.
The derived theoritical model is further analyzed numerically using empirical system parameters and compared with previous studies in Sec. \ref{sec_manipulate_conductivity}, followed by concluding remarks in Sec. \ref{sec_conclusions}.

### 2021-07-25 paper/v1.0/sections/3_floquet_theory.tex
Formatting and corrections
Corrections for abstract and introduction

The general interpretations of physical systems are mostly derived using symmetry conditions in quantum theory. Famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation of quantum systems occupying a discrete translational symmetry in configuration space. Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}. Examine the transport properties of quantum systems exposed to strong radiation using the Floquet-Drude conductivity method introduced recently by M. Wackerl \textit{et al.} \cite{wackerl20}. In their analysis they have presented more accurate results than previously existed theoretical descriptions for the conductivity of nanoscale systems in presence of a dressing field. Therefore, we are hoping to apply the Floquet-Drude conductivity method to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.

@@

Then performing Fourier transform over the confined two-dimentional space, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
\begin{equation} \label{eq_9}
  \begin{aligned}
    \phi_{n,m}\big(k_x,k_y,t\big)  = &
    {\sqrt{L_x}}
    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
    & \times
    \text{exp}\left(
      i\xi
      -ik_y  \qty[d\sin(\omega t) + y_0]
    \right),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_10}
  \tilde{\chi}_{n}\qty(k) =
  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
  \qty(\frac{1}{\kappa})^{1/2}
  e^{-\frac{k^2}{2 \kappa^2}}
  \mathcal{H}_{n} \qty(\frac{k}{\kappa}).
\end{equation}
Here we used new parameters
\begin{equation} \label{eq_11}
  b \equiv
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad \text{and} \quad
  d \equiv
 \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
\end{equation}
For details of the full derivation please refer to Appendix B. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in momentum space as Floquet states
\begin{equation} \label{eq_12}
  \psi_{n,m}(k_x,k_y,t) =
  \exp(-\frac{i}{\hbar}\varepsilon_{n}t)   \phi_{n,m} (k_x,k_y,t).
\end{equation}

>>>>

The general interpretations of physical systems are mostly derived using symmetry conditions in quantum theory. Famous Bloch analysis of electrons in quantum systems introduces a mathematical explanation of quantum systems occupying a discrete translational symmetry in configuration space. Floquet theory gives a mathematical formalism that can be used for translational symmetry in time rather than in space \cite{floquet83,grifoni98,holthaus15}. Examine the transport properties of quantum systems exposed to strong radiation using the Floquet-Drude conductivity method introduced recently by Wackerl \textit{et al.} \cite{wackerl20}. In their analysis they have presented more accurate results than previously existed theoretical descriptions for the conductivity of nanoscale systems in presence of a dressing field. Therefore, we are hoping to apply the Floquet-Drude conductivity method to analyze our 2DEG system which is subjected to both a stationary magnetic field and a dressing field.

@@

Then performing Fourier transform over the confined two-dimensional space, we obtain the momentum space($k_x,k_y$) representation of Floquet modes
\begin{equation} \label{eq_9}
  \begin{aligned}
    \phi_{n,m}\big(k_x,k_y,t\big)  = &
    {\sqrt{L_x}}
    \tilde{\chi}_{n}\qty(k_y - b\cos(\omega t)) \\
    & \times
    \text{exp}\left(
      i\xi
      -ik_y  \qty[d\sin(\omega t) + y_0]
    \right),
  \end{aligned}
\end{equation}
where
\begin{equation} \label{eq_10}
  \tilde{\chi}_{n}\qty(k) =
  \frac{i^n}{\sqrt{2^{n} n! \sqrt{\pi}}}
  \qty(\frac{1}{\kappa})^{1/2}
  e^{-\frac{k^2}{2 \kappa^2}}
  \mathcal{H}_{n} \qty(\frac{k}{\kappa}).
\end{equation}
Here we used new parameters
\begin{equation} \label{eq_11}
  b \equiv
  \frac{eE\omega_0^2}{\hbar\omega(\omega_0^2 - \omega^2)} \quad \text{and} \quad
  d \equiv
 \frac{eE}{m_e(\omega_0^2 - \omega^2)}.
\end{equation}
For details of the full derivation please refer to Appendix \ref{appendix_b}. Now using Floquet theory, the wave functions derived in Eq.~(\ref{eq_2}) can be written in momentum space as Floquet states
\begin{equation} \label{eq_12}
  \psi_{n,m}(k_x,k_y,t) =
  \exp(-\frac{i}{\hbar}\varepsilon_{n}t)   \phi_{n,m} (k_x,k_y,t).
\end{equation}

### 2021-07-25 paper/v1.0/sections/5_floquet_drude_conductivity.tex
Corrections for abstract and introduction

A general theory for the conductivity in dressed systems with the disorder averaging was introduced by M. Wackerl in Refs.~\cite{wackerl20,wackerlthesis20}. Within this theory, the general $x$-directional longitudinal DC limit conductivity can be express with
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} &=
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg],
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ the Fourier component (see Appendix \ref{appendix_d}) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system. Here we have assumed that only $s=0$ Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considering two-dimentional system, partial distribution function is given by $f$ and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq_21}
    \Pi- \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \frac{\hbar \omega}{2},
\end{equation}
where $ \varepsilon_N$ are quasienergies of all considering Floquet states.

>>>>

A general theory for the conductivity in dressed systems with the disorder averaging was introduced by M. Wackerl in Refs.~\cite{wackerl20,wackerlthesis20}. Within this theory, the general $x$-directional longitudinal DC limit conductivity can be express with
\begin{equation} \label{eq_20}
  \begin{aligned}
    {\sigma}^{xx} &=
    \frac{-1}{4\pi\hbar A}
    \int_{\Pi-\hbar\omega/2}^{\Pi+ \hbar\omega/2} d\varepsilon \bigg[
    \qty(
    -\frac{\partial f}{\partial \varepsilon})
    \\
    & \times
    \tr
    \qty[
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    {j}^x_0
    \qty(
    \vb{G}^{r} (\varepsilon) - \vb{G}^{a} (\varepsilon)
    )
    ]\bigg],
  \end{aligned}
\end{equation}
where ${j}^x_0$ and $\vb{G}^{r,a} (\varepsilon)$ are $x$-directional electric current operator matrix elements' $s=0$ the Fourier component (see Appendix \ref{appendix_d}) and white noise disorder averaged Floquet Green function matrix \cite{wackerl20,wackerlthesis20} respectively defined against the Floquet modes of the considering system. Here we have assumed that only $s=0$ Fourier component of the current operator is contributing to the conductivity. In addition, $A$ is the area of the considering two-dimensional system, partial distribution function is given by $f$ and $\Pi$ is a function that can be chosen such that
\begin{equation} \label{eq_21}
    \Pi- \frac{\hbar \omega}{2}
    \leq \varepsilon_N
    <
    \Pi + \frac{\hbar \omega}{2},
\end{equation}
where $ \varepsilon_N$ are quasienergies of all considering Floquet states.

### 2021-07-25 paper/v1.0/sections/6_manipulate_conductivity.tex
Corrections for abstract and introduction

To identify the characteristics of the longitudinal conductivity of the quantum Hall systems with external dressing field, first we can derive an expression for a normalized
longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$. Here we have the normalized x-directional conductivity using the natural conductivity of the least Landau level
\begin{equation} \label{eq_35}
  \begin{aligned}
    \frac{\sigma^{xx}}{\sigma^{0}} = &
    \sum_{n}
    \frac{\qty(n+1)}{0.0037\Lambda_n \Lambda_{n+1}} \\
    & \times
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n -1}{0.06\Lambda_n})^2
      }
    ]
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n}{0.06\Lambda_{n+1}})^2
      }
    ],
  \end{aligned}
\end{equation}
where $\sigma^0 = (e^2/\pi \hbar A)$. We use this expression to illustrate the changes that can be done to the longitudinal conductivity in 2DEG using external dressing field. As given in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the longitudinal conductivity $\sigma_{xx}$ using external dressing field's intensity and the Fermi level $X_F$ of the considering system. For a given dressing field intensity, the longitudinal conductivity vary against the Fermi level of the system by creating sharp peaks at each Landau level energy values. Since electrons are restricted to have only Landau level energies, the conductivity gets very low values when the Fermi level is not align with any of the Landau level energy values. In contrast, on each Landau level, the conductivity can achieve very high values compared to other areas and as illustrates on Fig.~\ref{fig_5} the peak value of longitudinal conductivity on each Landau level gets increase with the Landau level number.

@@

Considering the effect of the external dressing field on longitudinal conductivity of 2DEG, we can identify that high intensities shrink the conductivity regions near Landau levels. However, the peak value of the conductivity at each Landau level has the same value as the undressed system. This demonstrate that we are able to tune the width of the regions of conductivity in these quantum Hall systems with the help of a dressing field.
These characteristics are aligned with results demonstrated by K. Dini \textit{et al.} \cite{dini16} and as they remarked since the Fermi level of the system can be change with the applied gate voltage of the material this can be used as a 2D switch for nanoscale optoelectronics applications. Controlling  the external dressing field we are able to fine-tune the switching mechanism for optimized performance.
Furthermore, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig_5} and \ref{fig_6} are generally incompatible with the results reported in Ref.~\cite{dini16}. This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}. The semi-elliptical conductivity regions illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistence with the experimentally observed Landau levels representation \cite{endo09}.
In our study on the transport properties of quantum Hall systems, we developed the conductivity expression starting from Floquet-Drude conductivity \cite{wackerl20} and our results are much more align with the result mentioned in Ref. \cite{endo09}.
The description of conductivity of quantum Hall systems demonstrated in Ref.~\cite{endo09} has excellent agreement between the theory and experiment obtained in a GaAs/AlGaAs 2DES for the low magnetic field range. However, they have not considered the tunability that can be achieved with the external strong dressing field. In this analysis we account both magnetic and dressing field effects that can be applied into the transport properties of 2DEG, and we have presented a more generalized theory. As a concluding remark, in this study we were able to demonstrate that using Floquet-Drude conductivity method one can derive a more experimental fitting and generalized mathematical model that describes the transport properties of quantum Hall systems.

>>>>

To identify the characteristics of the longitudinal conductivity of the quantum Hall systems with external dressing field, first we can derive an expression for a normalized
longitudinal conductivity as a function of Fermi energy $X_F$ and intensity of the dressing field $I$. Here we have the normalized x-directional conductivity using the natural conductivity of the least Landau level
\begin{equation} \label{eq_35}
  \begin{aligned}
    \frac{\sigma^{xx}}{\sigma^{0}} = &
    \sum_{n}
    \frac{\qty(n+1)}{0.0037\Lambda_n \Lambda_{n+1}} \\
    & \times
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n -1}{0.06\Lambda_n})^2
      }
    ]
    \qty[
      \frac{1}
      {
        1 + \qty(\frac{X_F - n}{0.06\Lambda_{n+1}})^2
      }
    ],
  \end{aligned}
\end{equation}
where $\sigma^0 = (e^2/\pi \hbar A)$. We use this expression to illustrate the changes that can be done to the longitudinal conductivity in 2DEG using an external dressing field. As given in Fig.~\ref{fig_5} and \ref{fig_6} we can manipulate the longitudinal conductivity $\sigma_{xx}$ using an external dressing field's intensity and the Fermi level $X_F$ of the considering system. For a given dressing field intensity, the longitudinal conductivity vary against the Fermi level of the system by creating sharp peaks at each Landau level energy values. Since electrons are restricted to have only Landau level energies, the conductivity gets very low values when the Fermi level is not aligned with any of the Landau level energy values. In contrast, on each Landau level, the conductivity can achieve very high values compared to other areas and as illustrates in Fig.~\ref{fig_5} the peak value of longitudinal conductivity on each Landau level gets increase with the Landau level number.

@@

Considering the effect of the external dressing field on the longitudinal conductivity of 2DEG, we can identify that high intensities shrink the conductivity regions near Landau levels. However, the peak value of the conductivity at each Landau level has the same value as the undressed system. This demonstrates that we are able to tune the width of the regions of conductivity in these quantum Hall systems with the help of a dressing field.
These characteristics are aligned with results demonstrated by Dini \textit{et al.} \cite{dini16} and as they remarked since the Fermi level of the system can be changed with the applied gate voltage of the material this can be used as a 2D switch for nanoscale optoelectronics applications. Controlling  the external dressing field we are able to fine-tune the switching mechanism for optimized performance.
Furthermore, we can distinguish that the shapes and behavior of the conductivity regions illustrated in Fig.~\ref{fig_5} and \ref{fig_6} are generally incompatible with the results reported in Ref.~\cite{dini16}. This is due to the selection of the conventional longitudinal conductivity theory of 2DEG from Refs.~\cite{ando74_1,ando82}. The semi-elliptical conductivity regions illustrated in Refs.~\cite{dini16,ando74_1,ando82}, have less consistency with the experimentally observed Landau levels representation \cite{endo09}.
In our study on the transport properties of quantum Hall systems, we developed the conductivity expression starting from Floquet-Drude conductivity \cite{wackerl20} and our results are much more aligned with the result mentioned in Ref. \cite{endo09}.
The description of conductivity of quantum Hall systems demonstrated in Ref.~\cite{endo09} has an excellent agreement between the theory and experiment obtained in a GaAs/AlGaAs 2DES for the low magnetic field range. However, they have not considered the tunability that can be achieved with the external strong dressing field. In this analysis, we account for both magnetic and dressing field effects that can be applied to the transport properties of 2DEG, and we have presented a more generalized theory. As a concluding remark, in this study, we were able to demonstrate that using Floquet-Drude conductivity method one can derive a more experimental fitting and generalized mathematical model that describes the transport properties of quantum Hall systems.

### 2021-07-25 paper/v1.0/sections/7_conclusions.tex
Corrections for abstract and introduction

In this analysis, we reported a generalized mathematical model for transport properties in a 2DEG under a nonoscillating magnetic field and a high intensity light. With the uniform magnetic field, the charged particles can only settle in discrete energy values and this leads to the Landau quantization. We modelled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method by accounting impurities in the material as Gaussian random scattering potential. Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.

Our derived analytical expressions disclosed that the transport characteristics of the dressed quantum Hall system can be controlled by the applied dressing field’s intensity. Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field. We found that the graphical illustrations we gained are capable of produce the same behavior as the experiment conductivity found in quantum Hall systems without a dressing field. Furthermore, we identified that by regulating the intensity of the radiation, the conductivity regions near the Landau levels can be squeezed. Despite, this behavior has been identified previous works, their results are not coincide with the more accurate description of conductivity components in undressed quantum Hall systems. However, our generalized analysis of conductivity in dressed quantum Hall system provides well-suited description for these special quantum Hall systems.

In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties in dressed quantum Hall systems and our  detailed theoretical analysis shows that we were able to demonstrate that recently introduced Floquet-Drude conductivity model can be adopted to extend the models that are used to describe the transport characteristics in quantum Hall systems. Due to owing the ability of controlling the conductivity regions, high intensity external illumination can be used as a trigger for two-dimentional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices. Finally, we identified that our findings of this paper can be used towards understanding nanoscale quantum devices, enhancing their performance and inventing novel appliance.

>>>>

In this analysis, we reported a generalized mathematical model for transport properties in a 2DEG under a nonoscillating magnetic field and a high intensity light. With the uniform magnetic field, the charged particles can only settle in discrete energy values and this leads to the Landau quantization. We modeled the behavior of electrons in Landau levels under the dressing field utilizing the Floquet-Drude conductivity method by accounting impurities in the material as Gaussian random scattering potential. Finally, we derived expressions for x-directional and y-directional longitudinal components of electric conductivity tensor for the considered system.

Our derived analytical expressions disclosed that the transport characteristics of the dressed quantum Hall system can be controlled by the applied dressing field’s intensity. Using detailed numerical calculations with empirical system parameters, we further analyzed the manipulation of conductivity components using the dressing field. We found that the graphical illustrations we gained are capable of produce the same behavior as the experiment conductivity found in quantum Hall systems without a dressing field. Furthermore, we identified that by regulating the intensity of the radiation, the conductivity regions near the Landau levels can be squeezed. Despite, this behavior has been identified in previous works, their results are not coinciding with the more accurate description of conductivity components in undressed quantum Hall systems. However, our generalized analysis of conductivity in dressed quantum Hall system provides well-suited description for these special quantum Hall systems.

In summary, the primary purpose of this study was to broaden the modern descriptions on transport properties in dressed quantum Hall systems and our  detailed theoretical analysis shows that we were able to demonstrate that the  recently introduced Floquet-Drude conductivity model can be adopted to extend the models that are used to describe the transport characteristics in quantum Hall systems. Due to owing the ability to control the conductivity regions, high intensity external illumination can be used as a trigger for two-dimensional quantum switching devices which are employed as the building blocks of next generation nanoelectronic devices. Finally, we identified that our findings of this paper can be used towards understanding nanoscale quantum devices, enhancing their performance, and inventing novel appliances.
